---
title: "p8105_hw6_jl5549"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(modelr )
```

# Problem1
```{r}
birthweight = read_csv(file = './data/birthweight.csv') %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         momage = as.factor(momage)) %>% 
  drop_na()
head(birthweight)
```

```{r}
mymodel =step(lm(bwt ~ ., data = birthweight), direction = "backward")
summary(mymodel)
#a plot of model residuals against fitted values
birthweight %>% 
  add_predictions(mymodel) %>% 
  add_residuals(mymodel) %>% 
  ggplot(aes(x = pred, y = resid))+
  geom_point(col = 'brown') +
  geom_line(stat = "smooth", method = "lm")
broom::glance(mymodel)
```

```{r}
cv_df =
  birthweight %>% 
  crossv_mc(.,n = 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) 
cv_df= 
  cv_df%>% 
  mutate(
    model1 = map(train, ~lm(bwt~ wtgain*fincome, data = .)),
    model2 = map(train, ~lm(bwt~blength+gaweeks, data = .)),
    model3 = map(train, ~lm(bwt~bhead*blength*babysex, data= .))
    ) %>% 
  mutate(rmse_mymodel = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
cv_df %>% 
  select(starts_with('rmse')) %>%
  pivot_longer(everything(),
    names_to = 'model',
               values_to = 'rmse',
               names_prefix = 'rmse_')%>% 
  mutate(model= factor(model, levels = c('mymodel', 'model2', 'model3'))) %>% 
  ggplot(aes(x= model , y = rmse))+
  geom_violin()
```

## Problem 2
```{r}
#import the data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
#boostrap datasets and build model for each
weather_models = 
weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax~tmin, data = .x))) 
#tidy the models and extract statistics
estimates = 
  weather_models%>% 
  mutate(results = map(models, broom::tidy)) %>% 
  select(-models, -strap) %>% 
  unnest(results) %>% 
  pivot_wider(values_from = 'estimate',
              names_from = 'term') %>%
  janitor::clean_names() 
#extract beta0 and beta1
intercept = 
  estimates %>% 
   select(intercept, id) %>% 
   drop_na()
tmin = 
  estimates %>% 
   select(tmin, id) %>% 
   drop_na()
#calculate log(β̂ 0∗β̂ 1)
beta = inner_join(intercept, tmin, by = "id") %>% 
  mutate(log_beta01 = log(intercept*tmin))
#distribution of log(β̂ 0∗β̂ 1)
beta %>% 
  ggplot(aes(x =log_beta01))+
  geom_density()+
  labs(x = 'log(estimated beta0 *estimated beta1)')
```

```{r}
#2.5% and 97.5% quantiles
q1_log_beta01= quantile(beta$log_beta01, 0.025)
q2_log_beta01 = quantile(beta$log_beta01, 0.975)
# construct CIs
se_log_beta01 = sd(beta$log_beta01)/sqrt(length(beta$log_beta01))
mean_log_beta01 = mean(beta$log_beta01)
CI_log_beta01 = c(mean_log_beta01 - qnorm(0.975)*se_log_beta01,
                  mean_log_beta01 + qnorm(0.975)*se_log_beta01)
CI_log_beta01
```

```{r}
#find r^ 2
r2 =   
  weather_models%>% 
  mutate(results = map(models, broom::glance)) %>% 
  select(-models, -strap) %>% 
  unnest(results) %>% 
  janitor::clean_names()
r2 %>% 
  ggplot(aes(x = r_squared))+
  geom_density()
#2.5% and 97.5% quantiles
q1_r2= quantile(r2$r_squared, 0.025)
q2_r2= quantile(r2$r_squared, 0.975)
# construct CIs
se_rsquared = sd(r2$r_squared)/sqrt(length(r2$r_squared))
mean_rsquared = mean(r2$r_squared)
CI_rsquared = c(mean_rsquared - qnorm(0.975)*se_rsquared,
                  mean_rsquared + qnorm(0.975)*se_rsquared)
CI_rsquared
```
#identify the rows for 2.5% and 97.5% quantiles
row_q1 = 
  beta %>% 
  arrange(log_beta01) %>% 
  .[round(length(.$log_beta01)*0.025),]

row_q2 = 
  beta %>% 
  arrange(log_beta01) %>% 
  .[round(length(.$log_beta01)*0.975),] 
row_q1$id[1]
# construct CIs

data_q1 = 
  weather_models %>% 
  filter(.id == row_q1$id[1]) %>% 
  pull(strap) %>% 
  as.data.frame() 
CI_q1=
  data_q1 %>% 
  c(mean(.$tmin)-qnorm(0.975)*sd(.$tmin)/sqrt(length(.$tmin)),
   mean(.$tmin)+qnorm(0.975)*sd(.$tmin)/sqrt(length(.$tmin)))
CI_2= 
weather_models %>% 
  filter(id == row_q2$id[1]) %>% 
  c(mean(strap$tmin)-qnorm(0.975)*sd(strap$tmin)/sqrt(length(strap$tmin)),
   mean(strap$tmin)+qnorm(0.975)*sd(strap$tmin)/sqrt(length(strap$tmin)))
